Temperature, wave exposure and wind as drivers of morphology in two kelp species

### 2019-07-11 paper_morph_new.Rmd
minor edits to rmd script. Data house cleaning

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r Temperature data prep, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r Temperature variables plot, echo=FALSE, fig.cap="Temperature variables at the collection sites around the Cape Peninsula. Temperature variables include minimum represented by blue dots.", fig.height=9, fig.width=7}

@@

```{r Wave variable processing, include=FALSE}

@@

```{r Wave variable plot, echo=FALSE, fig.cap='Wave variables at each collection site around the Western Cape coast. Mean variables are represented by dots and standard deviation by whiskers. Plot "A" represents annual significant wave height.', fig.height=8, fig.width=8}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
```

@@

```{r Temperature data prep, message=FALSE, warning=FALSE, include=FALSE}

@@

```{r Temperature variables plot, echo=FALSE, include = FALSE, fig.cap="Temperature variables at the collection sites around the Cape Peninsula. Temperature variables include minimum represented by blue dots.", fig.height=9, fig.width=7}

@@

```{r Wave variable processing, warning=FALSE, include=FALSE, echo = FALSE}

@@

```{r Wave variable plot, echo=FALSE, fig.cap='Wave variables at each collection site around the Western Cape coast. Mean variables are represented by dots and standard deviation by whiskers. Plot "A" represents annual significant wave height.', fig.height=8, fig.width=7}
